The Design, Semantics, and Implementation of the Synchronous Language \CEU

### 2016-03-26 paper.tex
...

We completely missed the "finalize" construct of Esterel and recognize the 
similarity with our proposal.
We now emphasize that Céu tracks pointers entering and leaving the program to 
enforce appropriate use of "finalize" (as part of the section about interfacing 
with C).

@@

>>>>

@@

Since loops in \CEU must contain \code{await} statements, reactions run in 
bounded time, which guarantees that successive calls to \code{dispatch} never 
block the scheduler for long.
However, the code generation phase does not inspect C calls and also has no 
extra analysis such as for worst-case reaction 
times~\cite{esterel.wcrt,esterel.fixed}.
